### 2017-02-15 R/ITHIM.Rmd
sumDALY -> deltaBurden

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
document("~/ITHIM/")
#install("~/ITHIM/")
install_github("syounkin/ITHIM", ref="devel")
install_github("smbache/magrittr", ref="master")

@@

  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(State = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}

@@

deltaDALYList <- mapply(sumDALY, ITHIMList, ITHIMListScenario)

@@

    DALYs <- sumDALY(ITHIM.national, ITHIM.scenario)
    DALYs.quints <- sumDALY(ITHIM.national.quints, ITHIM.scenario.quints)

>>>>

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
document("~/ITHIM/")
install("~/ITHIM/")
#install_github("syounkin/ITHIM", ref="cambridge")
install_github("smbache/magrittr", ref="master")

@@

  DALYs <- lapply(ITHIMList, deltaBurden, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(State = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}

@@

deltaDALYList <- mapply(deltaBurden, ITHIMList, ITHIMListScenario)

@@

    DALYs <- deltaBurden(ITHIM.national, ITHIM.scenario)
    DALYs.quints <- deltaBurden(ITHIM.national.quints, ITHIM.scenario.quints)
